\module{compulsory}
{lecture, excercises and laboratory}
{German}
{12}
{360 h}
{\paragraph{Lecture General and Inorganic chemistry:} atomic theory, stoichiometry, chemical formulas, chemical reaction equations, energy turnover in chemical reactions, electron structure of atoms, properties of atoms, chemical bonding, ionic bonding, covalent bonding, molecular structure, molecular orbitals, properties of gases, liquids and solids, solutions, chemical equilibrium, acids and bases, solubility product, redox reactions.
\paragraph{Lecture Organic Chemistry: } Hybridization, atom and molecular orbitals, chemical equilibria, kinetics, classes of substances, functional groups, nomenclature, Substance properties, occurrence, synthesis and reactions, alkanes, alkenes, alkynes, isomerism, mesomerism, tautomerism, conformation, stereochemistry, haloalkanes, alcohols, ethers, carbonyl compounds, aldehydes, ketones, acetals, carboxylic acids, anhydrides, esters, amides, Nitriles, heterocycles, aromatics, radical, addition, elimination, substitution reactions, oxidation, reduction. The theoretical knowledge acquired in the lectures will then be intensified and applied in a compact practical course.
\paragraph{Lecture Biochemistry:} Basic knowledge of the structure of biologically relevant macromolecules as well as mechanistic and regulatory basic principles of metabolism (biosyntheses of sugars , complex carbohydrates, amino acids, proteins, fatty acids, lipids and the corresponding pathways) of eukaryotes. In addition, the basics of enzymology and modern biochemical techniques are taught.}
{The students know basic principles and techniques of general, inorganic and organic chemistry. They know the practical application of these concepts. You have experience with chemical work in the laboratory and are familiar with laboratory safety.}
{None}